### 2013-07-03 mcmc.tex
notes to self
give the no-sample-likelihood it's own section

@@

@@

...Priors: If you describe your priors in one parameterization but
then perform sampling in a different space, it is easy to make
mistakes.  For example: Flat prior in amplitude and phase, sample in
$A\,\cos\phi$ and $A\,\sin\phi$.  There are many ways to do this
wrong.

>>>>

\section{Likelihoods and priors}

@@

...It is a good idea to have proper priors.
It is a good test of your priors that you can sample with a ``null'' likelihood function.
You can often have your priors wrong despite having beautiful code.

...You must describe your priors in the same parameterization that you ``step'' in.
That is, if you change your parameters, you \emph{must} change your priors correspondingly.
Give the example of going from $A$, $\phi$ to $A\,\cos\phi$, $A\,\sin\phi$.

@@

...Priors: Once again:
If you describe your priors in one parameterization but
then perform sampling in a different space, it is easy to make
mistakes.  For example: Flat prior in amplitude and phase, sample in
$A\,\cos\phi$ and $A\,\sin\phi$.  There are many ways to do this
wrong.

...Posteriors: On the other hand, you can do anything you like (within
reason) to the output samples and be sampling the posterior in that
transformed quantity.
